---
title: "Package Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi=100
)
```

```{r setup}
library(MATH4753F25julianMoreno)
```

# Introduction
This package contains functions and R related files which were built with the instructor in class. 


# birthday
## Description
This code gives the probability that two people have the same birthday, given a number of people
## Source
```{r}
body(birthday)
```

## Demonstration
```{r}
birthday(20:25)
```


# ntickets
## Description
This function helps decide the optimal number of tickets a travel agency should sell to maximize seats sold and minimize overbooking, given the number of seats available, probability of overbooking occuring, and probability any given person shows up
## Source
```{r}
body(ntickets)
```
## Demonstration
```{r fig.height = 4,fig.width = 8}
par(mar = c(2,2,3,2)) # Unrelated to the code, this is just to make sure the figure shows in this document
ntickets(400,0.02,0.95)
```

# myncurve
## Description
Given a mean, variance for a normal distribution, and a lower tail probability, a graphical representation of the lower tail probability on the normal distribution is made.

## Source
```{r}
body(myncurve)
```

## Demonstration
```{r}
myncurve(0.2,0.5,0.3)
```


# myfirstfunction
## Description
Discrete given values are taken into a function, squaring the value, and plotted onto a graph.

## Source
```{r}
body(myfirstfunction)
```

## Demonstration
```{r}
myfirstfunction(1:10)
```
